Ames Housing: 허위매물 탐지 프로젝트

### 2025-04-24 group1.qmd

--- 
title: "Ames Housing: 허위매물 탐지 프로젝트"
author: '일단잡1조(송성필, 홍주형, 편서영, 양현준)'
format: 
  dashboard:
    theme: sandstone
    scrolling: True
    logo: igotyou.png
    freeze: true
---

>>>>

--- 
title: "Ames Housing: 허위매물 탐지 프로젝트"
author: '일단잡1조(송성필, 홍주형, 편서영, 양현준)'
format: 
  dashboard:
    theme: sandstone
    scrolling: True
    logo: project/group1_project/imagebox/nofakehouse.png
    freeze: true
---
